---
title: "Data Dictionary::"
output: 
  flexdashboard::flex_dashboard:
    theme: cerulean
    orientation: rows
    vertical_layout: fill
runtime: shiny

---


```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(visdat)
library(dplyr)
library(dygraphs)
library(DT)

library(plotly)



# ::Function

basic_info_table_2 <- function(my_df)
{
  tibble::tibble(
    `Variable Name` = names(my_df),
    `Datatype` = purrr::map_chr( my_df, function(x){ paste(class(x), collapse=' ')} ),
    `Number Unique Values` = purrr::map_int( my_df, n_distinct ),
    `Number Missing Values` = purrr::map_int( my_df, ~sum( is.na(.) ) )
  ) %>% 
    mutate(`Proportion Unique` = `Number Unique Values` / nrow(my_df),
           `Proportion Missing` = `Number Missing Values` / nrow(my_df)
           ,
           `Description` = ""
           )
}



#data choice
info<-reactive({
  if( input$data_option == 'Sample_data' ){
      option <- iris
    }else{
      option <-vroom::vroom(input$file1$datapath, locale = vroom::locale(encoding = "CP1252"))
    }
    option

})



  

d_table<-reactive({ 
  info()%>%basic_info_table_2()%>%
  DT::datatable(
    editable = TRUE,
    extensions = c('Buttons', 'Scroller'), 
   options = list( dom='Blrtip',
    buttons = c('copy', 'print', 'excel','pdf'),
    lengthMenu = list( c (-1, 50), c("All", 50))
  ))%>%
  DT::formatStyle(columns = colnames(.), fontSize = '10pt')
  })
  




# raw_table<-reactive({ 
#   info()%>%
#   DT::datatable(
#     editable = TRUE,
#     extensions = c('Buttons', 'Scroller'), 
#     options = list( dom='Blfrtip',
#     buttons = c('copy', 'print', 'csv', 'excel','pdf'),
#     lengthMenu = list( c (50,-1), c(50,"All"))
#     
#   ))%>%
#   DT::formatStyle(columns = colnames(.), fontSize = '10pt')
#   })




preview<-reactive({info() %>% glimpse()}%>%
                    DT::datatable(
    editable = TRUE,
    extensions = c('Buttons', 'Scroller'), 
    options = list( dom='Blfrtip',
    buttons = c('copy', 'print', 'csv', 'excel','pdf'),
    lengthMenu = list( c (50,-1), c(50,"All"))
    
  ))%>%
  DT::formatStyle(columns = colnames(.), fontSize = '10pt')
                    )

```



# 1. Import Data >> {data-icon="fa-database"}


Column {.sidebar}
-----------------------------------------------------------------------
<h5>1. Prepare Data before Using this App</h5>
<ul>
<li>CSV file is required</li>
<li>Keep your datatype consistent in the same field </li>
<li>Keep cells blank for intentional null data </li>
<li>Use the first rows to indicate the name of the field</li>
</ul>

<h5>2. Import Data</h5>
```{r}
radioButtons('data_option',"Select the data to use:",
            selected = 'Sample_data',choices = c("Sample_data", 'Upload_CSV'))
            
fileInput("file1", "Choose CSV File", multiple = TRUE,
          accept = c("text/csv", ".csv"))
```
<h5>3. Confirm data</h5>
<p>Confirm your data and navigate to <code>2. Data Dictionary</code></p>

<br></br>
<hr />

<p><sub>Questions</sub></p>
<p><sub>If you have any questions, please contact me via <a href="mailto:yem7@pitt.edu">yem7@pitt.edu</a> or <a href="mailto:muny@duq.edu">muny@duq.edu</a>.</sub></p>
-----------------------------------------------------------------------

Row {data-height=650}
-----------------------------------------------------------------------
### Preview

```{r}
renderDT({preview()})
```


# 2. Data Dictionary >> {data-icon="fa-table"}

Column {.sidebar}
-----------------------------------------------------------------------

<span data-preserver-spaces="true"><h5>1. Confirm Metadata</span></h5>
<p style="padding-left: 40px;"><span data-preserver-spaces="true">See if variable name, datatype, number of unique values, number of missing values, proportion of unique, and proportion of missing are correct.</span></p>
<br></br>
<h5>2. Edit Cells</h5>
<p style="padding-left: 40px;"><span data-preserver-spaces="true">The final column is for a longer explanation of the variable. Consider adding a description of the variable. It could help others to understand what the variable refers to. If you want to modify metadata, double-click the corresponding cell and rewrite the data.</span></p>
<br></br>
<h5>3. Export Data Dictionary</h5>
<p style="padding-left: 40px;"><span data-preserver-spaces="true">Once ready, you can export the data dictionary as a new file using buttons at the top (CSV, Excel, or PDF) .</span></p>
<p>&nbsp;</p>



Row {data-height=650}
-----------------------------------------------------------------------
### Info Table

```{r}
renderDT({d_table()})
```



-----------------------------------------------------------------------

# 3. Observation >> {data-icon='fa-check'}

Column {.sidebar}
-----------------------------------------------------------------------
<h5>Final Overview</h5>
<p>Confirm your data has appropriate datatype and missingness.</p>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------
### datatype

```{r}
renderPlot({
  p1<-info() %>% visdat::vis_dat(.,warn_large_dat =FALSE)+
      scale_fill_viridis_d()+coord_flip()
  p1
  })
```


### missingness

```{r}
renderPlot({
    p2<-info() %>% visdat::vis_miss(.,warn_large_dat =FALSE)+
      scale_fill_viridis_d()+coord_flip()
    p2
  })
```


